Approximation as Differentiation: Notes

### 2025-05-25 main/higher-order.tex
Set-wide products. If C has biproducts and set-wide products, then C is CC.

Although $\Fam(\FinVect)$ nor $\Fam(\LatGal)$ provide an appropriate notion of composition for automatic
differentiation and Galois slicing respectively, neither is Cartesian closed. Both are therefore unsuitable
for interpreting higher-order programs. However the following is a special case of a construction due to
\citet{nunes2023}:

>>>>

$\Fam(\FinVect)$ nor $\Fam(\LatGal)$ provide appropriate notions of composition for automatic differentiation
and Galois slicing respectively, but neither is Cartesian closed. Both are therefore unsuitable for
interpreting higher-order programs. However the following is a special case of a construction due to
\citet{nunes2023}:
